---
title: "SupWat"
author: "supwat"
date: "2/3/2018"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE}
library("tidyverse")
library("plyr")
library("dplyr")
library("magrittr")
library("gdata")
library("ggplot2")
library("plotly")
library("maps")
library("reshape2")
library("GGally")
     
load("final-graphs.Rda")
load("data/irs_edu_13.Rda")
```

#How Did Income Affect Education in Tennessee in the 2014 - 2015 Academic Year?

map of Tennessee's counties.
```{r agi_by_county, echo = F}
plot(agi_by_county)
```

  In 2016 **ACT** [reported](http://www.act.org/content/dam/act/unsecured/documents/R1604-ACT-Composite-Score-by-Family-Income.pdf) that students from families with an annual income of \$80,000 or more tend to score about four (4) points higher than their counterparts in families that earn less than \$80,000 a year. In 2013 the national average ACT composite score was 20.9. With ACT scores being a major (if not the primary) criteria for college admission in the US, a four (4) point difference is a big difference!

## "Wealth Bubbles""
### Wealth Distribution Across TN
  Using the *2013 IRS Tax Return Data* we can plot a bubble for each (inhabited) zipcode in TN. And we can:
  * make the bubbles larger according to the IRS's population estimates for 2013
  * darker according to each zipcode's Adjuste Gross Income per capita (County AGI divided by County Population). 


```{r corr_matrix, echo=FALSE,fig.width=17, fig.height=16}
plot(corr_matrix)
```
```{r combo_chloro, echo=FALSE, fig.width=17, fig.height=10}
plot(combo_chloro)
```
```{r agi_county_prc, echo=FALSE}
plot(agi_county_prc)
```
```{r top_5_agi_facet, echo=FALSE}
plot(top_5_agi_facet)
```
```{r bot_5_agi_facet, echo=FALSE}
plot(bot_5_agi_facet)
```
```{r act_agi_per_return, echo=FALSE}
plot(act_agi_per_return)
```
```{r act_agi_irs, echo=FALSE}
plot(act_agi_irs)
```

```{r act_counties, echo=FALSE, fig.width=20, fig.height=17}
plot(act_counties)
```
```{r final_corr, echo=FALSE}
plot(final_corr)
```
```{r act, echo=FALSE,fig.width=14, fig.height=3}
plot(act)
```
```{r ppe, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe)
```
```{r ppe_over_exp, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe_over_exp)
```
```{r ppe_over_agi, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe_over_agi)
```