---
title: "SupWat"
author: "supwat"
date: "1/30/2018"
output: html_document
---

```{r setup, echo=FALSE, include=FALSE}
library("tidyverse")
library("plyr")
library("dplyr")
library("magrittr")
library("gdata")
library("ggplot2")
library("plotly")
library("maps")
library("reshape2")
library("GGally")
     
load("final-graphs.Rda")
```

# Overview

Objective: to investigate possible correlation between ACT test results and financial status

#### Background
Claim: Family income can impact ACT score results

*<https://www.huffingtonpost.com/2014/07/18/act-score-family-income_n_5600065.html>*

#### Question
Does higher income result in better results in ACT?

# Methodology
#### 1. Databases used
1.1. IRS data for year 2013, grouped by zipcode

1.2. Results for educational performance, grouped by counties

1.3. An interim database to ‘bridge’ between educational results and IRS data

#### 2. Procedures
2.1. Summarizing data based on counties for IRS and education information

2.2. Merging data

2.3. Data visulization

* Plotting data over map

* Investigating correlations
* Individual plotting

```{r corr_matrix, echo=FALSE,fig.width=17, fig.height=16}
plot(corr_matrix)
```
```{r combo_chloro, echo=FALSE, fig.width=17, fig.height=10}
plot(combo_chloro)
```
```{r agi_county_prc, echo=FALSE}
plot(agi_county_prc)
```
```{r top_5_agi_facet, echo=FALSE}
plot(top_5_agi_facet)
```
```{r bot_5_agi_facet, echo=FALSE}
plot(bot_5_agi_facet)
```
```{r act_agi_per_return, echo=FALSE}
plot(act_agi_per_return)
```
```{r act_agi_irs, echo=FALSE}
plot(act_agi_irs)
```

```{r act_counties, echo=FALSE, fig.width=20, fig.height=17}
plot(act_counties)
```
```{r final_corr, echo=FALSE}
plot(final_corr)
```
```{r act, echo=FALSE,fig.width=14, fig.height=3}
plot(act)
```
```{r ppe, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe)
```
```{r ppe_over_exp, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe_over_exp)
```
```{r ppe_over_agi, echo=FALSE,fig.width=14, fig.height=3}
plot(ppe_over_agi)
```
