---
title: "MOSAIC Study Progress"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: cosmo
---

<style>                     
.navbar {
  background-color:#003D79;
  border-color:white;
}
.navbar-brand {
color:white!important;
}
</style>   

<style type="text/css">

.chart-title {  /* chart_title  */
   font-size: 15px

</style>

```{r setup, include=FALSE}
library(flexdashboard)
library(plotly)
library(highcharter)
library(treemap)
library(knitr)
library(devtools)

```

Screening & Enrollment
=====================================

Column {data-width=700}
-----------------------------------------------------------------------

### Patients Screened, Approached, and Enrolled

```{r}

```

### Study Exclusions (% of All Patients Excluded)

```{r}

```

Column {data-width=300}
-----------------------------------------------------------------------

### Cumulative Enrollment as of {data-height=250}

```{r}

```

### Approach & Refusal {data-height=250}


### Cumulative Exclusions {data-height=500}

```{r}

```

In-Hospital
=====================================

Column {data-width=500}
-----------------------------------------------------------------------

### Pre-Hospital Questionnaires {data-height=40}

### Prehospital Surrogate Battery Completion Rate

```{r}

```

```{r}

```

### Prehospital Caregiver Battery Completion Rate

```{r}

```

### Specimen Log Compliance (% of Patients Eligible)

```{r}

```

### Current In-Hospital Status

```{r}

```

Column {data-width=500}
-----------------------------------------------------------------------
### **Accelerometer Central** {data-height=40}

### Accelerometer Snapshot: Patient-Days

```{r}
```

### Accelerometer Snapshot: Patients

```{r}

```

### On Days Accelerometer Was Removed, How Many Times?

```{r}

```

### Reasons for Accelerometer Removal

```{r}

```

Follow-Up
=====================================

Column {data-width=650}
-----------------------------------------------------------------------

### Chart A

```{r}

```

Column {data-width=350}
-----------------------------------------------------------------------

### Chart B

```{r}

```

### Chart C

```{r}

```

Study & Technical Info
=====================================

MOSAIC is funded by the National Institutes of Health. Please see our listing on [clinicaltrials.gov](https://clinicaltrials.gov/ct2/show/NCT03115840).

This dashboard uses. Packages:

```{r}

```